% !TeX program = lualatex
% !BIB program = biber
% !TeX spellcheck = en_UK
% !TeX encoding = utf8
% !TeX root = ../ClaudioDiCiccio-CV.tex
%
%
\CvEntryDate{20/11/2025}%
\CvEntryDesc{%
	\CvDocTitle{Declarative process specification mining: Discovery of and reasoning on temporal-logic rules} at KU Leuven, Belgium.%
}%
%
\CvEntryDate{20/11/2025}%
\CvEntryDesc{%
	\CvDocTitle{Blockchain technologies for process management} at KU Leuven, Belgium.%
}%
%
\CvEntryDate{30/04/2025}%
\CvEntryDesc{%
	\CvDocTitle{Preserving secrecy for process data exchange via public blockchain}, Sapienza Cybersecurity Seminars, Sapienza University of Rome, Italy.%
}%
%
\CvEntryDate{21/06/2024}%
\CvEntryDesc{%
	\CvDocTitle{Declarative process specification mining: discovering and reasoning on temporal-logic rules}, VvL Dutch Logic PhD Day 2024, Vrije Universiteit (VU) Amsterdam, The Netherlands.%
}%
%
\CvEntryDate{11/04/2024}%
\CvEntryDesc{%
	\CvDocTitle{Declarative process specification mining}, Latin American School on Process Variability and Mining, Universidad de la Rep\'{u}blica, Uruguay.%
}%
%
\CvEntryDate{16/01/2024}%
\CvEntryDesc{%
	\CvDocTitle{Formal foundations of process mining: A primer} at WU Vienna, Austria.%
}%
%
\CvEntryDate{06/02/2023}%
\CvEntryDesc{%
	\CvDocTitle{Specification mining and the program from the block} at Utrecht University, The Netherlands.%
}%
%
\CvEntryDate{13/09/2022}%
\CvEntryDesc{%
	\CvDocTitle{Recent advances in event log format standardisation -- An update from the XES Working Group}, BP-meet-IoT'22, 13 September 2022, M\"{u}nster, Germany.%
}%
%
\CvEntryDate{04/07/2022}%
\CvEntryDesc{%
\CvDocTitle{Process discovery III: Declarative process mining}, Process Mining Summer School, 4-8 July 2022, Aachen, Germany.%
}%
%
\CvEntryDate{09/03/2022}%
\CvEntryDesc{%
	\CvDocTitle{Blockchain as a process automation infrastructure}, Sapienza Cybersecurity Seminars, Sapienza University of Rome, Italy.%
}%
%
\CvEntryDate{24/01/2022}%
\CvEntryDesc{%
	\CvDocTitle{Blockchain: Concepts and applications}, 2nd online school on Smart Data Processing and Systems of Deep Insight, 24-28 January 2022, for the DESTINI H2020 Twinning project, organised by the Cyprus University of Technology, Limassol, Cyprus.%
}%
%
\CvEntryDate{24/11/2021}%
\CvEntryDesc{%
	\CvDocTitle{Blockchain and smart contracts: Infrastructure and platforms}, Cyber 4.0 Seminar at Confindustria CONNEXT 2021, Milan, Italy.%
}%
%
\CvEntryDate{12/10/2021}%
\CvEntryDesc{%
	\CvDocTitle{Blockchain: Concepts and research directions} for the DESTINI H2020 Twinning project, organised by the Cyprus University of Technology, Limassol, Cyprus.%
}%
%
\CvEntryDate{02/11/2021}%
\CvEntryDesc{%
	\CvDocTitle{Panel: Rethinking the input for process mining} in the role of moderator at the XES 2.0 Workshop of the 3rd Int.\ Conference on Process Mining (ICPM 2021), Eindhoven, The Netherlands.%
}%
%
\CvEntryDate{09/09/2021}%
\CvEntryDesc{%
\CvDocTitle{Panel: Is process technology ready for rare events?} in the role of moderator at the 19th Int.\ Conference on Business Process Management (BPM 2021), Rome, Italy.%
}%
%
\CvEntryDate{03/03/2021}%
\CvEntryDesc{%
\CvDocTitle{Blockchain and smart contracts: Infrastructure and platforms} at the Cyber 4.0 Seminar hosted by the Cyber 4.0 Cybersecurity Competence Center, Rome, Italy.%
}%
%
\CvEntryDate{08/10/2020}%
\CvEntryDesc{%
	\CvDocTitle{The process and the blockchain: A story of miners} at WU Vienna, Austria.%
}%
%
\CvEntryDate{19/07/2019}%
\CvEntryDesc{%
	\CvDocTitle{The Process and the blockchain: A story of miners} at Sapienza University of Rome, Italy.%
}%
%
\CvEntryDate{03/07/2019}%
\CvEntryDesc{%
	\CvDocTitle{Tracking workflows on the blockchain} at the ``Blockchain: Applications and Security'' Cyber Security Summer School 2019, Voore, Estonia.%
}%
%
\CvEntryDate{27/05/2019}%
\CvEntryDesc{%
	\CvDocTitle{Declarative specification of processes: Discovery and reasoning} at Sapienza University of Rome, Italy.%
}%
%
\CvEntryDate{15/04/2019}%
\CvEntryDesc{%
	\CvDocTitle{Declarative specification of processes: Discovery and reasoning} at Utrecht University, The Netherlands.%
}%
%
\CvEntryDate{12/04/2019}%
\CvEntryDesc{%
	\CvDocTitle{Declarative specification of processes: Discovery and reasoning} at the Eindhoven University of Technology, The Netherlands.%
}%
%
\CvEntryDate{19/12/2018}%
\CvEntryDesc{%
	\CvDocTitle{An introduction to process mining} at the Technical University of Vienna (TU Wien), Austria.%
}%
%
\CvEntryDate{13/11/2018}%
\CvEntryDesc{%
	\CvDocTitle{How to execute business processes on the blockchain} at the Process Management Summit of the Gesellschaft f\"ur Prozessmanagement, Vienna, Austria, 13 November 2018.%
}%
%
\CvEntryDate{09/11/2018}%
\CvEntryDesc{%
	\CvDocTitle{Data Science $\times$ Business Process Management $=$ Process Mining} at the 16\textsuperscript{th} PQM Dialog (``Process Mining – Reale Prozesse im Fokus''), FH Kufstein, Austria, 9 November 2018.%
}%
%
\CvEntryDate{04/10/2018}%
\CvEntryDesc{%
	\CvDocTitle{Declarative business processes: Discovery and reasoning} at the Seminars of the University of Wollongong, NSW, Australia, 4 October 2018.
}%
%
\CvEntryDate{25/09/2018}%
\CvEntryDesc{%
	\CvDocTitle{Declarative business processes: Discovery and reasoning} at the CIS Seminars of the University of Melbourne, VIC, Australia.%
}%
%
\CvEntryDate{14/08/2018}%
\CvEntryDesc{%
	\CvDocTitle{Tracking business processes on the blockchain} at Dagstuhl Seminar 18332 (``Blockchain Technology for Collaborative Information Systems''), Schloss Dagstuhl, Germany, 12--17 August 2018.%
}%
%
\CvEntryDate{08/02/2018}%
\CvEntryDesc{%
	\CvDocTitle{Paradigm-independence of metrics} at the Brainstorm Seminar Conformance Checking Metrics, Maasmechelen, Belgium, 8 February 2018.%
}%
%
\CvEntryDate{14/03/2018}%
\CvEntryDesc{%
	\CvDocTitle{Data Science $+$ BPM} at the Data Science Society Kick-off event, Vienna, Austria, 14 March 2018.%
}%
%
\CvEntryDate{17/11/2017}%
\CvEntryDesc{%
	\CvDocTitle{The application of process analytics in the field of smart logistics: Examples from airfreight and road transportation} at the University of Edinburgh, United Kingdom.%
}%
%
\CvEntryDate{28/09/2017}%
\CvEntryDesc{%
	\CvDocTitle{Logistics data: Analysis, mining, and execution on blockchain} at the European Supply Chain Forum's Data2Move kick-off meeting, 28-29 September 2017, Eindhoven, The Netherlands.%
}%
%
\CvEntryDate{06/03/2017}%
\CvEntryDesc{%
	\CvDocTitle{The application of process analytics in the field of smart logistics: Examples from airfreight and road transportation} at CSIRO/Data61, Sydney, Australia.%
}%
%
\CvEntryDate{07/12/2016}%
\CvEntryDesc{%
	\CvDocTitle{Automated discovery of declarative process models} at the Humboldt-Universit\"at zu Berlin, Germany.%
}%
%
\CvEntryDate{13/09/2016}%
\CvEntryDesc{%
	\CvDocTitle{Introduction to process mining} at the Federal University of the State of Rio de Janeiro, Brazil.%
}%
%
\CvEntryDate{25/08/2016}%
\CvEntryDesc{%
	\CvDocTitle{Predictive task monitoring: Processing flight events to foresee diversions} at Dagstuhl Seminar 16341 (``Integrating Process-Oriented and Event-Based Systems''), Schloss Dagstuhl, Germany, 21--26 August 2016.%
}%
%
\CvEntryDate{22/09/2015}%
\CvEntryDesc{%
	\CvDocTitle{The automated discovery of declarative processes} at the Workshop on the Presence and Future of Process Mining, Bratislava, Slovak Republic, 22-23 September 2015.%
}%
%
\CvEntryDate{15/09/2014}%
\CvEntryDesc{%
	\CvDocTitle{Automated control-flow discovery of declarative processes} at the Hasso-Plattner Institute, University of Potsdam, Germany.%
}%
%
\CvEntryDate{12/12/2013}%
\CvEntryDesc{%
	\CvDocTitle{Automated control-flow discovery of declarative processes} at the Eindhoven University of Technology, The Netherlands.%
}%
%
\CvEntryDate{09/12/2013}%
\CvEntryDesc{%
	\CvDocTitle{Flight diversion prediction based on event data} at the Eindhoven University of Technology, The Netherlands.%
}%
