% !TeX program = lualatex
% !BIB program = biber
% !TeX spellcheck = en_UK
% !TeX encoding = utf8
% !TeX root = ../ClaudioDiCiccio-CV.tex
%
\CvEntryDate{15/10/2024}%
\CvEntryDesc{%
	\CvDocTitle{A Taste of the Different Flavors of Tiramis\`{u}}~\cite{Alman.etal/ICPM-D2024:TasteDifferentFlavorsTiramisu} at the Demo Track of the 6th International Conference on Process Mining (ICPM 2024), Copenhagen, Denmark.%
}%
\CvEntryDate{03/06/2024}%
\CvEntryDesc{%
	\textbf{Keynote}: \CvDocTitle{{\guillemotleft}I'm still / I'm still / Chaining from the Block{\guillemotright}: An Outlook of the Ongoing and Future Relationship between Blockchain Technologies and Process-aware Information Systems.}  joint workshop on Blockchain for Information Systems (BC4IS) and Blockchain for Trusted Data Sharing (B4TDS), co-located with the 36th International Conference on Advanced Information Systems Engineering (CAiSE), Limassol, Cyprus.%
}%
%
\CvEntryDate{13/09/2023}%
\CvEntryDesc{%
	\textbf{Keynote}: \CvDocTitle{Look but don't touch: On the impalpable bond between blockchain and process} at the 4th BPM Blockchain Forum, Utrecht, Netherlands.%
}%
%
\CvEntryDate{19/08/2023}%
\CvEntryDesc{%
	\textbf{Keynote}: \CvDocTitle{Automated reasoning and data analytics for declarative process mining} at the 2nd Workshop on Process Management in the AI Era (PMAI), co-located with the 32nd International Joint Conference on Artificial Intelligence (IJCAI 2023), Macao S.A.R.%
}%
%
\CvEntryDate{27/10/2022}%
\CvEntryDesc{%
	\CvDocTitle{Measurement of rule-based {LTL}f declarative process specifications}~\cite{Cecconi.etal/ICPM2022:MeasurementLTLfSpecifications}, at the 4th Int.\ Conference on Process Mining ({ICPM} 2022), Bolzano, Italy, October 23-28, 2022.%
}%
%
\CvEntryDate{14/09/2022}%
\CvEntryDesc{%
	\CvDocTitle{Conformance checking of mixed-paradigm process models}~\cite{Dongen.etal/IS2021:ConformanceCheckingMixedParadigmProcessModels}, poster at the 20th Int.\ Conference on Business Process Management ({BPM} 2022), M{\"{u}}nster, Germany, September 11-16, 2022.%
}%
%
\CvEntryDate{23/07/2022}%
\CvEntryDesc{%
	\CvDocTitle{Computing unsatisfiable cores for LTLf specifications}~\cite{Roveri.etal/PMAI2022:UnsatisfiableLTLfCores}, at the Workshop on Process Management in the {AI} Era ({PMAI} 2022) co-located with IJCAI, Vienna, Austria, July 23, 2022.%
}%
%
\CvEntryDate{08/09/2021}%
\CvEntryDesc{%
	\CvDocTitle{RuM: Declarative process mining, distilled}~\cite{Alman.etal/BPM2021:RuMDeclarativeProcessMiningDistilled}, tutorial at the 19th Int.\ Conference on Business Process Management (BPM), Rome, Italy, 2021, 6-10 September 2021.%
}%
%
\CvEntryDate{11/11/2020}%
\CvEntryDesc{%
	\textbf{Keynote}: \CvDocTitle{Mining process rules from email} at the Automation, Control, and Analysis of Knowledge-intensive Processes Workshop, hosted by the IBM CASCON~x~EVOKE conference, Toronto, Canada.%
}%
%
\CvEntryDate{08/06/2020}%
\CvEntryDesc{%
\CvDocTitle{Business process monitoring on blockchains -- Potentials and challenges}~\cite{DiCiccio.etal/BPMDS2020:BusinessProcessMonitoringonBlockchains} at the 21st International Working Conference on Enterprise, Business-Process and Information Systems Modeling (BPMDS 2020), co-located with CAiSE, Grenoble, France,
8-9 June 2020.%
}%
%
\CvEntryDate{19/02/2020}%
\CvEntryDesc{%
	\CvDocTitle{Towards a process-oriented analysis of blockchain data}~\cite{DiCiccio/MOD-DLT2020:TowardsProcessOrientedAnalysisBlockchainData} at the 1st Int.\ Workshop on Conceptual Modeling for Distributed Ledger Technologies (MOD-DLT), co-located with Modellierung, Vienna, Austria, 19 February 2020.%
}%
%
\CvEntryDate{02/09/2019}%
\CvEntryDesc{%
	\CvDocTitle{Extracting event logs for process mining from data stored on the blockchain}~\cite{Muehlberger.etal/SPBP2019:ExtractingEventLogsfromBlockchain} at the 2nd Int.\ Workshop on Security and Privacy-enhanced Business Process Management (SPBP 2019), co-located with BPM, Vienna, Austria, 2 September 2019.%
}%
\CvEntryDate{01/07/2018}%
\CvEntryDesc{%
	\CvDocTitle{Blockchain-based traceability of inter-organisational business processes}~\cite{DiCiccio.etal/BMSD2018:BlockchainBasedTraceabilityBusinessProcesses} at the 8th Int.\ Symposium on Business Modeling and Software Design (BMSD 2018), Vienna, Austria, 2-4 July 2018.%
}%
\CvEntryDate{13/06/2017}%
\CvEntryDesc{%
	\CvDocTitle{Resolving inconsistencies and redundancies in declarative process models}~\cite{DiCiccio.etal/IS2017:ResolvingInconsistenciesRedundanciesDeclare} at the 8th Int.\ Workshop on 
	Enterprise Modeling and Information Systems Architectures (EMISA 2017), Essen, Germany, 12-13 June 2017.%
}%
% EMISA 
\CvEntryDate{03/10/2016}%
\CvEntryDesc{%
	\CvDocTitle{Detecting flight trajectory anomalies and predicting diversions in freight transportation}~\cite{DiCiccio.etal/DSS2016:PredictingDiversions} at the 7th International Workshop on 
	Enterprise Modeling and Information Systems Architectures (EMISA 2016), Vienna, Austria, 3-5 October 2016%
}%
% EMISA
\CvEntryDate{20/09/2016}%
\CvEntryDesc{%
	\CvDocTitle{Semantical vacuity detection in declarative process mining}~\cite{Maggi.etal/BPM2016:SemanticalVacuityDetectionDeclare} at the 14th Int.\ Conference on Business Process Management (BPM 2016), Rio de Janeiro, Brazil, 18-22 September 2016.%
}%
\CvEntryDate{19/09/2016}%
\CvEntryDesc{%
	\CvDocTitle{Model checking of mixed-paradigm process models in a discovery context -- Finding the fit between declarative and procedural}~\cite{DeSmedt.etal/BPI2016:ModelCheckingofMixedParadigmDiscovery} at the 12th Int.\ Workshop on Business Process Intelligence (BPI 2016), Rio de Janeiro, Brazil, 19 September 2016.%
}%
\CvEntryDate{01/09/2015}%
\CvEntryDesc{%
	\CvDocTitle{Ensuring model consistency in declarative process discovery}~\cite{DiCiccio.etal/BPM2015:EnsuringModelConsistency}~\AwardWIco{\citeAward{DiCiccio.etal/BPM2015:EnsuringModelConsistency}}, Innsbruck, Austria, 31 August - 3 September 2015.%
}%
\CvEntryDate{29/10/2014}%
\CvEntryDesc{%
	\CvDocTitle{Log-based understanding of business processes through temporal logic query checking}~\cite{Raeim.etal/CoopIS2014:LogBasedUnderstanding} at the 22nd Int.\ Conference on Cooperative Information Systems (CoopIS 2014), Amantea, Italy, 27-31 October 2014.%
}%
\CvEntryDate{10/09/2014}%
\CvEntryDesc{%
	\CvDocTitle{Discovering target-branched Declare constraints}~\cite{DiCiccio.etal/BPM2014:DiscoveringTargetBranched} at the 12th Int.\ Conference on Business Process Management (BPM 2014), Eindhoven, Netherlands, 7-11 September 2014.%
}%
\CvEntryDate{08/09/2014}%
\CvEntryDesc{%
	\CvDocTitle{Predictive task monitoring for business processes}~\cite{Cabanillas.etal/BPM2014:PredictiveTaskMonitoring} at the 12th Int.\ Conference on Business Process Management (BPM 2014), Eindhoven, Netherlands, 7-11 September 2014.%
}%
\CvEntryDate{30/08/2013}%
\CvEntryDesc{%
	\CvDocTitle{Studies on the discovery of declarative control flows from error-prone data}~\cite{DiCiccio.Mecella/SIMPDA2013:StudiesDiscoveryDeclarative} at the 3rd Int.\ Symposium on Data-driven
	Process Discovery and Analysis (SIMPDA 2013), Riva del Garda, Italy, 30 August 2013.%
}%
\CvEntryDate{17/04/2013}%
\CvEntryDesc{%
	\CvDocTitle{A two-step fast algorithm for the automated discovery of declarative workflows}~\cite{DiCiccio.Mecella/CIDM2013:TwoStepFast} at the IEEE Symposium on Computational Intelligence and Data
	Mining (CIDM 2013), Singapore, 16-19 April 2013.%
}%
\CvEntryDate{14/09/2012}%
\CvEntryDesc{%
	\CvDocTitle{Goal-based composition of stateful services for smart homes}~\cite{DeGiacomo.etal/CoopIS2012:GoalBasedComposition} at the 20th Int.\ Conference on Cooperative Information Systems (CoopIS 2012), Rome, Italy, 10-14 September 2012.%
}%
\CvEntryDate{15/06/2012}%
\CvEntryDesc{%
	\CvDocTitle{Knowledge-intensive processes: An overview of contemporary approaches}~\cite{DiCiccio.etal/KiBP2012:KnowledgeintensiveProcesses} at the 1st Int.\ Workshop on Knowledge-intensive
	Business Processes (KiBP 2012), Rome, Italy, 15 June 2012.%
}%
\CvEntryDate{22/05/2012}%
\CvEntryDesc{%
	\CvDocTitle{Mining constraints for artful processes}~\cite{DiCiccio.Mecella/BIS2012:MiningConstraintsArtfulProcesses} at the 15th Int.\ Conference on Business Information Systems (BIS 2012), Vilnius, Lithuania, May 21-23 2012.%
}%
\CvEntryDate{25/11/2011}%
\CvEntryDesc{%
	\CvDocTitle{Representing and visualizing mined artful processes in MailOfMine}~\cite{DiCiccio.etal/HCI-KDD2011:RepresentingVisualizingDeclarativeModels} at the 7th Conference of the
	Workgroup Human-Computer Interaction and Usability Engineering of the Austrian Computer Society (USAB 2011), Graz, Austria, 25-26 November 2011.%
}%
\CvEntryDate{30/05/2011}%
\CvEntryDesc{%
	\CvDocTitle{MailOfMine -- Analyzing mail messages for mining artful collaborative processes}~\cite{DiCiccio.etal/SIMPDApp2012:MailOfMineAnalyzingMail} at the 1st Int.\ Symposium on Data-Driven Process Discovery and Analysis (SIMPDA 2011), Campione d'Italia, Italy, June 29 - July 1st 2011.%
}%
\CvEntryDate{24/03/2011}%
\CvEntryDesc{%
	\CvDocTitle{Service composition and advanced user interfaces in the home of tomorrow: the SM4All approach}~\cite{Catarci.etal/Ambi-Sys2011:ServiceCompositionSM4All} at the 2nd Int.\ ICST Conference on Ambient Media and Systems (AMBI-SYS 2011), Porto, Portugal, March 24-25 2011.%
}
