% !TeX program = lualatex
% !BIB program = biber
% !TeX spellcheck = en_UK
% !TeX encoding = utf8
% !TeX root = ../ClaudioDiCiccio-CV.tex
%
\CvEntryDate{2022--2023}
\CvEntryDesc{%
	\CvEntryEmpl{Research unit head}%
	\CvEntryEmplWhere{PRIN research project \CvDocTitle{exPlaInable kNowledge-aware PrOcess INTelligence (PINPOINT)}, grant number (CUP) B87G22000450001 with the Department of Computer Science of Sapienza University of Rome, Italy. Total funding:~\SI{794578}{€} (Sapienza:~\SI{182809}{€}).}%
}%
\CvEntryDate{2022--2023}
\CvEntryDesc{%
	\CvEntryEmpl{Research unit head}%
	\CvEntryEmplWhere{Cyber 4.0 competence centre research project \CvDocTitle{Blockchain register for Import Export (BRIE)}, core pillar framework, with the Department of Computer Science of Sapienza University of Rome, Italy. Total funding:~\SI{179000}{€} (Sapienza:~\SI{32000}{€}).}%
}%
\CvEntryDate{2023}
\CvEntryDesc{%
\CvEntryEmpl{Co-principal\\investigator}%
\CvEntryEmplWhere{PRIN research project \CvDocTitle{Panacea: A Model-Based Framework for Self-Protecting Systems}, grant number (CUP) B53D23013280006 with the Department of Computer Science of Sapienza University of Rome, Italy. Total funding:~\SI{238203}{€} (Sapienza:~\SI{78559}{€}).}%
}%
\CvEntryDate{2023}
\CvEntryDesc{%
\CvEntryEmpl{Co-principal\\investigator}%
\CvEntryEmplWhere{Sapienza research project \CvDocTitle{ASGARD: Autonomous and Self-Governing Agent-Based Rule Design} with the Department of Computer Science of Sapienza University of Rome, Italy. Funding:~\SI{47500}{€}.}%
}%
\CvEntryDate{2022--}
\CvEntryDesc{%
\CvEntryEmpl{Project coordinator\\Scientific advisor}%
\CvEntryEmplWhere{Lazio research and innovation project -- incentives for innovative doctoral programs for enterprises and the PA \CvDocTitle{Predictive process monitoring for production planning}, grant number (CUP) B83C22004050009 with the Department of Computer Science of Sapienza University of Rome, Italy. Funding:~\SI{72995}{€}.}%
}%
\CvEntryDate{2022--2023}
\CvEntryDesc{%
	\CvEntryEmpl{Faculty investigator}%
	\CvEntryEmplWhere{Sapienza research project \CvDocTitle{Distributed Ledger and Credit Guarantee Schemes} with the Departments of Computer Science and Management of Sapienza University of Rome, Italy. Funding:~\SI{33890}{€}.}%
}%
\CvEntryDate{2022--2023}
\CvEntryDesc{%
\CvEntryEmpl{Faculty investigator}%
\CvEntryEmplWhere{Sapienza research project \CvDocTitle{Drones as a Service for First Emergency Response} with the Department of Computer Science of Sapienza University of Rome, Italy. Funding:~\SI{45000}{€}.}%
}%
\CvEntryDate{2022}
\CvEntryDesc{%
	\CvEntryEmpl{Faculty host}%
	\CvEntryEmplWhere{Research visit program at the Department of Computer Science of Sapienza University of Rome, Italy, hosting Prof. Hajo A.\ Reijers. Total funding:~\SI{9000}{€}.}%
	}%
\CvEntryDate{2021--2023}
\CvEntryDesc{%
	\CvEntryEmpl{Faculty investigator}%
	\CvEntryEmplWhere{Sapienza research project \CvDocTitle{Secure and Privacy-preserving Protocols for Automatic Contact Tracing (SPECTRA)} with the Department of Computer Science of Sapienza University of Rome, Italy. Funding:~\SI{42000}{€}.}%
}%
\CvEntryDate{2021}
\CvEntryDesc{%
	\CvEntryEmpl{Faculty host}%
	\CvEntryEmplWhere{Research visit program with the Department of Computer Science of Sapienza University of Rome, Italy, hosting Dr. Artem Polyvyanyy. Total funding:~\SI{5000}{€}.}%
}%
\CvEntryDate{2017--2019}
%\CvEntryDate{10/2017--}
\CvEntryDesc{%
	\CvEntryEmpl{Work package leader}%
	\CvEntryEmplWhere{Austrian Research Promotion Agency (FFG) research project \CvDocTitle{Cyber-Physical Social Systems for City-wide Infrastructures} (CitySPIN), grant number 861213, with WU Vienna, Austria. Total funding:~\SI{628000}{€} (WU:~\SI{167000}{€}).
		\newline
		Lead of Work Package 5 (\CvDocTitle{Process Mining and Monitoring on Linked Data}).}
}%
\CvEntryDate{2015--2019}
%\CvEntryDate{05/2015--}
\CvEntryDesc{%
	\CvEntryEmpl{Work package leader}%
	\CvEntryEmplWhere{EU H2020 Marie Skłodowska-Curie research project \CvDocTitle{Propelling Business Process Management by Research and Innovation Staff Exchange} (RISE\_BPM), grant number 645751, with WU Vienna, Austria.  Total funding:~\SI{855000}{€} (WU:~\SI{252000}{€}).
		\CvWebUrl{https://cordis.europa.eu/project/id/645751}{cordis.europa.eu/project/id/645751}
		\newline
		Lead of Work Package 8 (\CvDocTitle{Synthesis of IT artifacts: BPM implementation}).}
}%
\CvEntryDate{2019}
\CvEntryDesc{%
	\CvEntryEmpl{Research partner}%
	\CvEntryEmplWhere{Austrian Research Promotion Agency (FFG) Competence Centers for Excellent Technologies (COMET) \CvDocTitle{Austrian Blockchain Center (ABC)}, Area 2 (Cryptoeconomic Modelling \& Blockchain Applications for Business), with WU Vienna, Austria. \CvWebUrl{https://www.blockchain-center.at/}{blockchain-center.at}}%
}
%
\CvEntryDate{2017--2018}
%\CvEntryDate{10/2017--01/2018}
\CvEntryDesc{%
	\CvEntryEmpl{Research staff member}%
	\CvEntryEmplWhere{Austrian Research Promotion Agency (FFG) research project \CvDocTitle{Business Process Optimization Toolkit}, grant number 862950, with WU Vienna, Austria.}%
}
%
\CvEntryDate{2014--2017}
%\CvEntryDate{10/2014--03/2017}
\CvEntryDesc{%
	\CvEntryEmpl{Research staff member}%
	\CvEntryEmplWhere{Austrian Research Promotion Agency (FFG) research project \CvDocTitle{Safety-critical Human- and dAta-centric Process management in Engineering projects} (SHAPE), grant number 861213, with WU Vienna, Austria.
		\CvWebUrl{https://ai.wu.ac.at/shape-project/}{ai.wu.ac.at/shape-project}}%
}%
%
\CvEntryDate{2013--2015}
%\CvEntryDate{07/2013--09/2015}
\CvEntryDesc{%
	\CvEntryEmpl{Research staff member}%
	\CvEntryEmplWhere{EU FP7-ICT research project \CvDocTitle{European Wide Service Platform for Green European Transportation} (GET Service), grant number 318275, with WU Vienna, Austria. 
		\CvWebUrl{https://cordis.europa.eu/project/id/318275}{cordis.europa.eu/project/id/318275}}%
}%
%
\CvEntryDate{2008--2011}
%\CvEntryDate{09/2008--08/2011}
\CvEntryDesc{%
	\CvEntryEmpl{Research staff member}%
	\CvEntryEmplWhere{EU FP7-ICT research project \CvDocTitle{Smart Homes for All} (SM4All), grant number 224332, with Sapienza University of Rome, Italy. 
		\CvWebUrl{https://cordis.europa.eu/project/rcn/87276/factsheet/en}{sm4all-project.eu}}%
}%
%
\CvEntryDate{2007--2008}
%\CvEntryDate{01/2007--06/2008}
\CvEntryDesc{%
	\CvEntryEmpl{Research assistant}%
	\CvEntryEmplWhere{\CvDocTitle{Re-engineered Province Bureaus [Uffici Provinciali Reingegnerizzati]} (UPR), research project funded by the Italian local authorities of Regione Lazio in collaboration with the Province of Latina (SM4All), with Sapienza University of Rome, Italy.%
	}%
}%
%
\CvEntryDate{2006--2007}
%\CvEntryDate{03/2006--09/2006}
\CvEntryDesc{%
	\CvEntryEmpl{Research technician}%
	\CvEntryEmplWhere{EU FP6 \CvDocTitle{DELOS Network of Excellence on Digital Libraries}, with Sapienza University of Rome, Italy.
		\CvWebUrl{http://delosw.isti.cnr.it/}{delosw.isti.cnr.it}%
	}%
}
%
\CvEntryDate{2018}
\CvEntryDesc{%
	\CvEntryEmpl{Referee}%
	\CvEntryEmplWhere{Register of Scientific Experts (REPRISE), Fundamental Research section, set up at the Italian Ministry of Education, University and Research%
	}%
}%
\CvEntryDate{2018}
\CvEntryDesc{%
	\CvEntryEmpl{Referee}%
	\CvEntryEmplWhere{The Netherlands' research council for the Engineering and Applied Sciences (NWO/TTW)%
	}%
}%
\CvEntryDate{2017}
\CvEntryDesc{%
	\CvEntryEmpl{Referee}%
	\CvEntryEmplWhere{Italian Research Projects of National Relevance (PRIN)%
	}%
}%