% !TeX program = lualatex
% !BIB program = biber
% !TeX spellcheck = en_UK
% !TeX encoding = utf8
% !TeX root = ../ClaudioDiCiccio-CV.tex
%
\CvEntryAcr{PhD}%
\CvEntryDesc{%
	\CvEntryRole{Supervisor}%
	\CvEntryAcrDesc{%
		\begin{inparaitem}
			\item \emph{Computer Science} at Sapienza University of Rome: 
			{4 candidates} (Luca~B., Dave~B., Valerio~G, Saba~L., starting between 2021 and 2022),
			and
			{1 PhD laureate} (Edo~M., 2025).
		\end{inparaitem} 
	}%
	\CvEntryRole{Co-supervisor}%
	\CvEntryAcrDesc{%
		\begin{inparaitem}
			\item \emph{Computing Sciences} at Utrecht University, The Netherlands:
			{2 candidates} (Michele~K., Marcus~D., starting in 2025).
			\item \emph{Business Informatics} at WU Vienna, Austria:
			{1 PhD laureate} (Alessio~C., 2022).
			\item \emph{Computer Science and Engineering} at Sapienza University of Rome, Italy:
			{1 PhD laureate} (Simone~A., 2022).
		\end{inparaitem} 
	}%
	\CvEntryRole{Daily advisor}%
	\CvEntryAcrDesc{%
		\begin{inparaitem}
			\item \emph{Business Informatics} at WU Vienna, Austria:
			{1 PhD candidate} (Johannes~P.) and
			{2 PhD laureates} (Anton~Y., Dina~B., 2022). 
		\end{inparaitem}
	}%
	\CvEntryRole{Examiner}%
	\CvEntryAcrDesc{%
		\begin{inparaitem}%
			\item \emph{Computer Science} at the University of Copenhagen, Denmark: {2 candidates} (Paul~C., 2024, and Christoffer~OB., 2021).
			\item \emph{Information and Communication Technology} at Sapienza University of Rome, Italy: {1 candidate} (Pierluigi~L., 2024).
			\item \emph{Information and Communication Technology} at Griffith University, Australia: {1 candidate} (Jeyakumar~ST., 2024).
			\item \emph{Computer Science and Mathematics} at the University of Camerino, Italy (Alessandro~M., 2023).
			\item \emph{Computer Science and Engineering} at the University of Seville, Spain (\'Alvaro~VP., 2022).
		\end{inparaitem}%
	}%
	\CvEntryRole{Co-author}%
	\CvEntryAcrDesc{%
		Published papers co-authored by the PhD candidates:
		\cite{%
			Cecconi.etal/IS2024:MeasuringRuleBasedLTLfSpecifications,%
			Bayomie.etal/IS2023:EventCaseCorrelation,%
			Basile.etal/FBloc2023:BlockchainResourceGovernanceDecentralizedWeb,%
			Yeshchenko.etal/TVCG2022:VisualDriftDetectionEventSequenceDataBusinessProcesses,%
			Cecconi.etal/IS2022:MeasuringTemporalLogicBehavioralSpecifications,%
			DiCiccio.etal/InfSpektrum2019:BlockchainSupportforCollaborativeBusinessProcesses,%
			DiCiccio.etal/DSS2016:PredictingDiversions,%
			Marcelletti.etal/BPMF2025:CONFETTY,%
			Dees.etal/EDOC2025:DNI,%
			Goretti.etal/ICSOC2025:ProMiSe,%
			Barbaro.etal/BPMF2025:Sp3llsWizard,%
			Basile.DiCiccio/BPM2025:SecrecyPreservationOnline,%
			Goretti.etal/ICPM-D2024:CONFINE,%
			Leo.etal/ICBT2024:TransformingCGSWithDLT,%
			Marangone.etal/CAiSEForum2024:CAKE,%
			Goretti.etal/CAiSE2024:TEEforProcessMining,%
			Marangone.etal/EDOC2023:MARTSIA,%
			Basile.etal/ICDCSw2023:BlockchaindrivenArchitecture,%
			Bayomie.etal/ICPM2022:EventCaseCorrelationRuleMining,%
			Cecconi.etal/ICPM2022:MeasurementLTLfSpecifications,%
			Marangone.etal/BPMBCF2022:AccessControlBlockchain,%
			Cecconi.etal/BPMF2021:VariantsThroughDeclarativeRules,%
			Cecconi.etal/ICPM2020:TLBasedMeasurementProcessMining,%
			Yeshchenko.etal/ICPM-D2020:VDD,%
			Azzam.etal/CPSSIoT2019:TheCitySPINPlatform,%
			DiCiccio.etal/CAiSEForum2019:DeclareNoncompliancesSemanticTechnologies,%
			Yeshchenko.etal/ER2019:ComprehensiveProcessDriftDetectionwithVisualAnalytics,%
			Bayomie.etal/ER2019:EventCaseCorrelationforProcessMining,%
			Yeshchenko.etal/ERdemos2019:ComprehensiveProcessDriftAnalysisVisualTool,%
			Cecconi.etal/BPM2018:Janus,%
			Cabanillas.etal/EMoV2014:TowardsPredictionEngine,%
			Cabanillas.etal/EMoV2014:CombiningEventProcessing,%
			Prescher.etal/SIMPDA2014:FromDeclarativeToImperative%
		}.
	}%
}%
\CvEntryAcr{MSc}%
\CvEntryDesc{%
	\CvEntryRole{Supervisor}%
	\CvEntryAcrDesc{%
		\begin{inparaitem}
			\item \emph{Computing Sciences} at Utrecht University:
			{1 thesis} (Floris~vVtV., 2025).
			\item \emph{Business Informatics} at Utrecht University:
			{1 thesis} (Mariia~K., 2025).
			\item \emph{Artificial Intelligence} at Utrecht University:
			{1 research internship} (Cecilia~I., 2025).
			\item \emph{Computer Science} at Sapienza University of Rome:
			{11 theses} (Michele~S., Fabiana~M., Marco~R., Nagarjun~L., Elvina~L., Vincenzo~R., Andrea~P., Tommaso~B., Dave~B., Valerio~G., Andrea~T., 2022-2024).
			\emph{Cybersecurity} at Sapienza University of Rome:
			{1 thesis} (Michele~K., 2024).
			\item \emph{Economics and communication for management and innovation} at Sapienza University of Rome:
			{3 theses} (Mariia~D., Emanuele~C., Dario~A., 2021-2022).
		\end{inparaitem} 
	}%
	\CvEntryRole{Co-supervisor}%
	\CvEntryAcrDesc{%
		\begin{inparaitem}%
			\item \emph{Business Informatics} at Utrecht University:
			{2 theses} (Alan~C., Christoffer~KG., 2025).
			\item \emph{Information Systems} at WU Vienna: 
			{4 theses} (Maxim~V., Dominik~H., Erwin~F., Roman~M., 2015-2020).
			\item \emph{Computer Science and Engineering} at Sapienza University of Rome:
			{3 theses} (Alessio~C., Vincenzo~F., Ettore~I., 2012-2018).
		\end{inparaitem}%
	}%
	\CvEntryRole{Examiner}%
	\CvEntryAcrDesc{%
		\begin{inparaitem}%
			\item \emph{Computer Science} at Sapienza University of Rome:
			{8 theses} (Mujtaba~HM., Giordano~D., Gabriella~T., Gianmarco~C., Luca~B., Andrei~SB., Alberto~M., Sanaz~E., 2020-2023).
			\item \emph{Computer Science} at the University of Padua, Italy:
			{1 thesis} (Guido~S., 2020).
		\end{inparaitem}%
	}%
	\CvEntryRole{Co-author}%
	\CvEntryAcrDesc{%
		Published papers co-authored by the MSc students:
		\cite{%
			DiCiccio.etal/ICSTTrans2011:HomesTomorrow,%
			Iacometta.DiCiccio/BPMDemos2025:MINERful,%
			Kryston.etal/CAiSEForum2025:MARTSIAToolConfidential,%
			Marangone.etal/CAiSEForum2024:CAKE,%
			Basile.etal/BPMBCF2021:BlockchainProcessesDecentralizedOracles,%
			Alman.etal/ICPM2020:RuM,%
			Alman.etal/ICPM-D2020:RuM,%
			Muehlberger.etal/BPMBCF2020:FoundationalOraclePatterns,%
			Muehlberger.etal/SPBP2019:ExtractingEventLogsfromBlockchain,%
			DiCiccio.etal/BMSD2018:BlockchainBasedTraceabilityBusinessProcesses,%
			Caruso.etal/SYROCO2012:ServiceEcologiesHome,%
			Catarci.etal/Ambi-Sys2011:ServiceCompositionSM4All%
		}.%
	}%
}
\CvEntryAcr{BSc}%
\CvEntryAcrDesc{%
	\CvEntryRole{Supervisor}%
	\CvEntryAcrDesc{%
		\begin{inparaitem}
			\item \emph{Information Sciences} at Utrecht University:
			{1 thesis} (Pelle~V., 2024).
			\item \emph{Applied Computer Science and Artificial Intelligence} at Sapienza University of Rome:
			{2 theses} (Cecilia~I., 2023, Alessandro~V., 2024).
			\item \emph{Computer Science} at Sapienza University of Rome:
			{14 theses} (Alexandru~C., Alessandro~C., Jessica~LC., Ralph~A., Matteo~M., Simone~Z., Michele~K., Mirko~P., Marco~R., Silverio~M., Seweryn~K., Emanuele~B., Dave~B., Valerio~G., Daniele~C., 2020-2024).
			\item \emph{Information Business} at WU Vienna, Austria:
			{14 theses} (Thomas~S., Mark~S., Daniel~W., Dominik~H., Daniel~E., Martin~C., Matej~P., Amra~N., Maximilian~K., Lukas~H., Michael~H., Asja~H., Tianhe~L., Julien~T.C., 2015-2019).
		\end{inparaitem} 
	}%
	\CvEntryRole{Co-supervisor}%
	\CvEntryAcrDesc{%
		\begin{inparaitem}
			\item \emph{Information Sciences} at Utrecht University:
			{2 theses} (Joris~K., Wahib~T., 2024-2025).
			\item \emph{Applied Computer Science and Artificial Intelligence} at Sapienza University of Rome:
			{2 theses} (Cecilia~I., Alessandro~V., 2023-2024).
			\item \emph{Computer Science} at Sapienza University of Rome:
			{15 theses} (Alexandru~C., Alessandro~C., Jessica~LC., Ralph~A., Matteo~M., Simone~Z., Michele~K., Mirko~P., Marco~R., Silverio~M., Seweryn~K., Emanuele~B., Dave~B., Valerio~G., Daniele~C., 2020-2024).
			\item \emph{Information Business} at WU Vienna, Austria:
			{14 theses} (Thomas~S., Mark~S., Daniel~W., Dominik~H., Daniel~E., Martin~C., Matej~P., Amra~N., Maximilian~K., Lukas~H., Michael~H., Asja~H., Tianhe~L., Julien~T.C., 2015-2019).
		\end{inparaitem} 
	}%%
	\CvEntryRole{Co-author}%
	\CvEntryAcrDesc{%
	Published papers co-authored by the BSc students:
	\cite{%
		Hanser.etal/STT2016:NewNotationalFrameworkDeclare,%
		Hanser.etal/ZEUS2016:NovelFrameworkVisualizingDeclare,%
		Puchovsky.etal/SIMPDA2016:BenefitsAutomatedProcessDiscovery%
	}.%
	}%
}%
%