\subsection*{Publications}
\begin{enumerate}
	\item \fullcite{DiCiccio.Montali/PMH2022:DeclarativeProcessMining}~\cite{DiCiccio.Montali/PMH2022:DeclarativeProcessMining}.
	\\[2ex]
	This book chapter is part of the teaching material for the first Process Mining Summer School, 4-8 July 2022, Aachen, Germany \CvWebUrl{http://www.process-mining-summer-school.org/}{process-mining-summer-school.org}. I had the pleasure and honour to be one of the lecturers, together with 20 speakers and more than 130 participants from all over the world. Together with Prof Marco Montali, we wrote the contribution above for the module about our main area of competence: \CvDocTitle{Process Discovery III: Declarative Process Mining}.
	\item \fullcite{DiCiccio.etal/IS2017:ResolvingInconsistenciesRedundanciesDeclare}~\cite{DiCiccio.etal/IS2017:ResolvingInconsistenciesRedundanciesDeclare}.
	\\[2ex] 
	This paper is the extended version of: \fullcite{DiCiccio.etal/IS2017:ResolvingInconsistenciesRedundanciesDeclare}~\cite{DiCiccio.etal/BPM2015:EnsuringModelConsistency}~\AwardWIco{\citeAward{DiCiccio.etal/BPM2015:EnsuringModelConsistency}}.
	As the corresponding author, I contributed to the writing of the paper and to the design, implementation, formalization and evalaution of the approach described therein.
\end{enumerate}
%
\subsection*{Algorithms}
\begin{enumerate}\setcounter{enumi}{2}
	\item MINERful \CvWebUrl{https://github.com/cdc08x/MINERful}{github.com/cdc08x/MINERful} \cite{DiCiccio.Mecella/CIDM2013:TwoStepFast}
	\\[2ex]
	To date, it is among the fastest tools for the discovery of process specifications from event logs. It is also the engine backing other process mining tools such as RuM~\cite{Alman.etal/BPM2021:RuMDeclarativeProcessMiningDistilled}. Its source is openly available and documented at the address above. I am the main contributor of this project.
\end{enumerate}
%
\subsection*{Teaching modules}
\begin{enumerate}\setcounter{enumi}{3}
	\item \CvDocTitle{Blockchain and Distributed Ledger Technologies} \CvWebUrl{https://sites.google.com/uniroma1.it/blockchain-dlt-course}{sites.google.com/uniroma1.it/blockchain-dlt-course}%
	\\[2ex]
	This course is part of the M.Sc.\ Programmes in \CvDocTitle{Computer Science} and \CvDocTitle{Cybersecurity} at the Sapienza University of Rome, Italy. It started in a.y.\ 2022-23 as a 6~ECTS course. I have created the whole structure, contents, slides, exercises, notes and evaluation scheme.
\end{enumerate}
%
\subsection*{Outreach activities}
\begin{enumerate}\setcounter{enumi}{4}
	\item \CvDocTitle{Blockchain -- Transforming Business} 
	\CvWebUrl{https://www.youtube.com/watch?v=p7fiwaDHqU0}{youtube.com/watch?v=p7fiwaDHqU0}%
	\\[2ex]
	This short program was part of the WU Executive Academy program. Held in Vienna, Austria, in May 2019, it has been among the first courses in Europe tailored for professionals specifically focussing on blockchain technologies and business applications. I was appointed academic director and lecturer.
\end{enumerate}
%
\subsection*{Organisation of events}
\begin{enumerate}\setcounter{enumi}{5}
	\item PC Chair of the Twentieth Int.\ Conference on Business Process Management (BPM 2022, \GGSRating{A})
	\\ \CvWebUrl{https://bpm2022.uni-muenster.de/}{bpm2022.uni-muenster.de}%
	\\[2ex]
	BPM is the premier conference in the area of Business Process Management. I was Track Chair of Track I (Foundations). The PC Co-Chairs were Remco Dijkman (Track II), Adela del R\'io Ortega (Track III), and Stefanie Rinderle-Ma (Consolidation Chair).
	%
	\item PC Chair of the third Int.\ Conference on Process Mining (ICPM 2021) 
	\\ \CvWebUrl{https://icpmconference.org/2021/}{icpmconference.org/2021}%
	\\[2ex]
	ICPM is the flagship conference on Process Mining, my core area of expertise. I was one of the three PC Chairs, together with Dr Chiara Di Francescomarino and Pnina Soffer.
\end{enumerate}
